{\large Gravitational wave sources in our Galactic backyard:}\\{\normalsize Models for detecting BHBH, BHNS and NSNS binaries with LISA

### 2021-11-24 paper/tex/sections/comparisons.tex
update comparison table

\begin{figure*}[p]
    \centering
    \includegraphics[width=\textwidth]{fig13_1_compare_dco.png}

@@

    \includegraphics[width=\textwidth]{fig13_2_compare_dco.png}
    \caption{A table comparing previous studies of a similar nature to this work. In the detection rate section darker shades of blue indicate higher detection rates. In other sections, darker shades of green indicate more detailed models or more accurate choices. Entries in detection rates with two values listed correspond to the different mission lengths (penultimate column). The works listed in the table are \citet{Nelemans+2001}, \citet{Belczynski+2010}, \citet{Liu+2014}, \citet{Lamberts+2018}, \citet{Sesana+2020}, \citet{Lau+2020}, \citet{Breivik+2020} and \citet{Shao+2021}. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig13_1_compare_dco.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig13_2_compare_dco.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/previous_BH_NS_studies.xlsx}{\faFileExcel}.}
    \label{fig:previous_studies}
\end{figure*}

>>>>

\begin{figure*}[p]
    \centering
    \includegraphics[width=\textwidth]{fig12_1_compare_dco.png}

@@

    \includegraphics[width=\textwidth]{fig12_2_compare_dco.png}
    \caption{A table comparing previous studies of a similar nature to this work. In the detection rate section darker shades of blue indicate higher detection rates. In other sections, darker shades of green indicate more detailed models or more accurate choices. Entries in detection rates with two values listed correspond to the different mission lengths (penultimate column). The works listed in the table are \citet{Nelemans+2001}, \citet{Belczynski+2010}, \citet{Liu+2014}, \citet{Lamberts+2018}, \citet{Sesana+2020}, \citet{Lau+2020}, \citet{Breivik+2020} and \citet{Shao+2021}. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig12_1_compare_dco.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig12_2_compare_dco.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/previous_BH_NS_studies.xlsx}{\faFileExcel}.}
    \label{fig:previous_studies}
\end{figure*}
